---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dbcti

<!-- badges: start -->
<!-- badges: end -->

The goal of dbcti is to support cell trajectory inference analysis for single-cell RNA-seq data. dbcti is designed to be able to infer any topological patterns of cell differentiation path and is robust to noises in single-cell RNA-seq data.

## System requirements
### Hardware Requirements
`dbcti` package is able to perform its operations on a standard computer.

### OS Requirements
The `dbcti` package should be compatible with Windows, Mac, and Linux operating systems. The package has been tested on the following systems:

* Linux 3.10.0
* Windows 10

### R Dependencies
`dbcti` depends on the following r package 
``` r
Rtsne,
FNN,
NMF,
MASS,
mclust,
princurve,
stringr,
igraph,
colorRamps,
rrcov,
grDevices,
methods
prada,
ggplot2
```
## Installation

The package dbcti is able to be installed from GitHub:

``` r
if (!require('devtools')) install.packages('devtools')
devtools::install_github('tianlt/dbcti')
```
The package should take approximately 1 minute to install on a recommended computer.

## Example

This is a basic example of using DBCTI:



```{r example, message=FALSE}
library(dbcti)

sample_data <- as.data.frame(sample_data)

#### Load data and create cell_trajectory project
sample_dbcti <- create_object(sample_data, normalized = TRUE) 

#### Filter data
sample_dbcti <- filter_data(sample_dbcti, gene_cri = 1, cell_cri = 1, use_normalized_data = TRUE) 


#### Feature selection
sample_dbcti <- select_var_feature(sample_dbcti, use_normalized_data = TRUE, n = 50)

#### Build tsne plot
sample_dbcti <- tsneplot(sample_dbcti, use_normalized_data = TRUE, specified_gene = FALSE, pca = TRUE, perplexity = 10)

#Build contour plot
sample_dbcti <- contour_plot(sample_dbcti)

#Estimate distribution
sample_dbcti <- distribution_estimation(sample_dbcti, ndraw = 100, expansion = 1.5, ... = 1,2,3) 

#Calculate possibility for points
sample_dbcti <- point_possibility(sample_dbcti, r = 5)

#Connect cluster
sample_dbcti <- connect_cluster(sample_dbcti)

#Infer_trajectory
sample_dbcti <- infer_trajectory(sample_dbcti, iter_n =15)

#Calculate pseudotime
sample_dbcti <- calculate_pseudotime(sample_dbcti, start_state_name = c('1','2'))

#Build trajectory plot
sample_dbcti <- plot_trajectory(sample_dbcti)

#Finally let's plot the trajectory
plot(sample_dbcti@trajectory_plot$plot)

#session info is also attached;
sessionInfo()
```



The demo should take approximately 1 minute to finish running on a standard computer.

## Issues and bug reports
Please use <https://github.com/tianlt/dbcti/issues> to submit issues, bug reports, and comments.



## License
DBCTI is distributed under the [GNU General Public License version 2 (GPLv2)](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html).



